Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-05-31 R0V0.tex
Remove the dependence of Y on u

\mypara Define $\Xi$ as the set of functions $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ with components defined by
\begin{equation*}
		Y_{ij}\begin{cases}
		=Y_{ij}(x_i,\vec{x}_i)u_i\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
		\equiv0_{m_i\times n_i},&\text{otherwise},
		\end{cases}
\end{equation*}
for every $i,j\in\mathscr{V}_c$, and for every $(x_i,\vec{x}_i,u_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}\times\mathbb{R}^{m_i}$.

@@

\mypara 	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
	\begin{equation}\label{eq:K ODE}
		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s))k^\ast(t,s)\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
	\end{equation}
which has a unique solution defined on a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$. It remains to show that this interval of existence can be extended on $[0,1]$. In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.

\mypara 	To show that a solution $k^\ast$ to Equation~\eqref{eq:K ODE} is defined on the whole interval $[0,1]$, the result  \cite[Theorem 2.12]{Teschl2012} is employed. This theorem states that, if the vector field has a linear growth with respect to the variable $k^\ast$, then solutions to \eqref{eq:K ODE} are defined on the whole interval $[0,1]$.

\mypara Since the vector field $\overline{K}$ is affine on $k^\ast$. This implies that, for every fixed $t\geq0$, and for every $S>0$, there exist constants $c_1(S)$ and $c_2(S)$ such that the inequality
	\begin{equation*}
		\left|\overline{K}(t,s,k^\ast)\right|\leq c_1(S)+c_2(S)|k^\ast|
	\end{equation*}
	holds, for every $(s,k^\ast)\in [-S,S]\times\mathbb{R}^m$. Applying \cite[Theorem 2.12]{Teschl2012} pointwisely with respect to $t\geq0$ implies that a solution $k^\ast$ to \eqref{eq:K ODE} is defined for every $s\in[0,1]$.

\mypara Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma))k_i^\ast(t,\sigma)\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}$. Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}.

>>>>

\mypara Define $\Xi$ as the set of functions $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ with components defined by
\begin{equation*}
		Y_{ij}\begin{cases}
		=Y_{ij}(x_i,\vec{x}_i)\in\mathbb{R}^{m_i\times n_i},&\text{if}\ (i,j)\in\mathscr{E}_c,\\
		\equiv0_{m_i\times n_i},&\text{otherwise},
		\end{cases}
\end{equation*}
for every $i,j\in\mathscr{V}_c$, and for every $(x_i,\vec{x}_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}$.

@@

\mypara Note that, due to the constraint $Y\in\Xi$, the independence of $Y$ with respect to the input variable $u$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(t,\sigma))\tfrac{\partial\widetilde{\gamma}_i}{\partial \sigma}(t,\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbb{R}^{n_i}\times\mathbb{R}^{\vec{n}_i}$. Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}.
